\bf\mftitle

### 2011-01-26 doc/jInfer/basicxsd/basicxsd.tex
just cite repair
fixed overfull hboxes by package names
Documenting BasicXSDExporter.

\documentclass[a4paper,10pt,oneside]{article}
\usepackage{graphicx}
\usepackage{color}
\usepackage{url}
\usepackage{subfigure}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{tgpagella}
%\usepackage[scale=0.9]{tgcursor}
%\usepackage[scale=0.9]{tgheros}

\newcommand{\myscale}{0.74}
\newcommand{\vect}[1]{\boldsymbol{#1}}
\newcommand{\code}[1]{\texttt{#1}}
\newcommand{\jmodule}[1]{\texttt{\textit{#1}}}

@@

The main class implementing \code{SchemaGenerator} inference interface and simultaneously registered as its service provider is \code{SchemaGeneratorImpl}. Process of export consists of two phases described in detail in later sections:
\begin{enumerate}
	\item Preprocessing
	\item Own export to string representation of XSD
\end{enumerate}
Method \code{start} first creates instance of \code{Preprocessor} class supplied by rules (elements) it got in the simplified grammar on input. Phase of preprocessing is done by creating that instance (calling its constructor) and its purpose is to discover information such which elements should be globally defined and which element is the top level element (TODO rio how is this element called in XML??).\\

Afterwards, it recursively traverses global elements followed by other elements starting at the top level element and for each it creates element's XSD string representation.\\

@@

TODO rio

@@

TODO rio\\

@@

Flow of data in this module is following.
\begin{enumerate}
	\item \code{SchemaGeneratorImpl} topologically sorts elements (rules) it got on input.
	\item For each element, relevant portion of DTD schema is generated.
	\item String representation of the schema is returned along with the information that file extension should be "dtd".
\end{enumerate}
\cite{ahonen}
%\nocite{*}
\newpage
\bibliographystyle{alpha}
\bibliography{literature}

>>>>

\documentclass[a4paper,10pt,oneside]{article}
\usepackage{graphicx}
\usepackage{color}
\usepackage{url}
\usepackage{subfigure}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{tgpagella}
%\usepackage[scale=0.9]{tgcursor}
%\usepackage[scale=0.9]{tgheros}
\usepackage{xstring}

\newcommand{\myscale}{0.74}
\newcommand{\vect}[1]{\boldsymbol{#1}}
\newcommand{\code}[1]{\texttt{\StrSubstitute{#1}{.}{.\.}}}
\def\.{\discretionary{}{}{}}
\newcommand{\jmodule}[1]{\texttt{\textit{#1}}}

@@

The main class implementing \code{SchemaGenerator} inference interface and simultaneously registered as its service provider is \code{SchemaGeneratorImpl}. Process of export consists of two phases described in detail in later sections:
\begin{enumerate}
	\item Preprocessing
	\item Own export to string representation of XSD
\end{enumerate}
Method \code{start} first creates instance of \code{Preprocessor} class supplied by rules (elements) it got in the simplified grammar on input. Phase of preprocessing is done by creating that instance (calling its constructor) and its purpose is to discover information such which elements should be globally defined and which element is the top level element (TODO rio how is this element called in XML??). This instance is kept as a member variable of module to be used during the whole export process.\\

Afterwards, \code{start} method recursively traverses global elements followed by other elements starting at the top level element and for each it creates element's XSD string representation.\\

@@

As mentioned before, preprocessing is implemented in \code{Preprocessor} class and its functions are following.
\begin{itemize}
	\item Decide which elements should be defined globally.
	\item Remove unused elements.
	\item Find the top level element.
	\item Find an instance of element by its name.
\end{itemize}

Constructor of \code{Preprocessor} class gets elements and a number, defining minimal number of occurrences of an element to be defined. It first topologically sorts input elements to decide which one is the top level element. Afterwards, it counts occurrences of the elements and removes unused ones (those which did not occurred). Finally, for each element it decides whether mark it as a global one or not. An element is considered global if its occurrence count is greater than or equal number of occurrences supplied on input.\\

Results of preprocessing are provided by public methods of \code{Preprocessor} class. For details see their JavaDoc.\\

@@

Own XSD export is performed in module's \code{start} function right after the preprocessing.\\

Useful helper class to handle indentation of text in a resulting XSD is named \code{Indentator}. Instance of this class is a member variable of the module (alike instance of \code{Preprocessor}), it holds text appended to it and keeps indentation level state. Text can be appended without indentation (method \code{append}) or indented (method \code{indent}). Level of indentation can be incremented or decremented by methods \code{increaseIndentation} and \code{decreaseIndentation}. At the end of export, when textual representation of each element has been appended to the \code{Indentator}, \code{Indentator}'s method \code{toString} will return string representation of resulting XSD.\\

First, global elements are exported. For each element, its type is defined as a global type. TODO rio example

After global elements, others are exported.

@@

Flow of data in this module is following.
\begin{enumerate}
	\item \code{SchemaGeneratorImpl} topologically sorts elements (rules) it got on input.
	\item For each element, relevant portion of DTD schema is generated.
	\item String representation of the schema is returned along with the information that file extension should be "dtd".
\end{enumerate}

\nocite{*}
\newpage
\bibliographystyle{alpha}
\bibliography{literature}
